Transform and Tell:\\The News Image Caption Writer That Remembers Rare Names

### 2019-11-13 paper/section_0_abstract.tex
Cite pointer-generator paper

%%%%%%%%% ABSTRACT
\begin{abstract}
    We propose an end-to-end model to generate image captions in news articles.
    By combining the transformer architecture, byte-pair encoding, and
    pretrained embeddings from three different modalities (RoBERTa for text,
    ResNet-152 for images, and FaceNet for faces), our system is able to
    describe an image with specific named entities mentioned in the article. Our
    model achieves a CIDEr score of 54 on the GoodNews dataset, significantly
    outperforming the previous state-of-art CIDEr of 13. We also introduce the
    NYTimes800k dataset, the largest news image captioning dataset to date.
    NYTimes800k is an extended version of GoodNews with higher-quality articles and
    metadata that allow us to study the importance of the image location within
    the text. On NYTimes800k, we achieve a CIDEr of 55. Pretrained models and
    source code are available from
    \href{https://github.com}{https://github.com/anonymized-link}.
 \end{abstract}

>>>>

%%%%%%%%% ABSTRACT
\begin{abstract}
    We propose an end-to-end model to generate image captions in news articles.
    By combining the transformer architecture, byte-pair encoding, copying with
    multi-headed attention, and pretrained embeddings from three different
    modalities (RoBERTa for text, ResNet-152 for images, and FaceNet for
    faces), our system is able to describe an image with specific named
    entities mentioned in the article. Our model achieves a CIDEr score of 54
    on the GoodNews dataset, significantly outperforming the previous
    state-of-art CIDEr of 13. We also introduce the NYTimes800k dataset, the
    largest news image captioning dataset to date. NYTimes800k is an extended
    version of GoodNews with higher-quality articles and metadata that allow us
    to study the importance of the image location within the text. On
    NYTimes800k, we achieve a CIDEr of 55. Pretrained models and source code
    are available from
    \href{https://github.com}{https://github.com/anonymized-link}.
 \end{abstract}

### 2019-11-13 paper/section_1_intro.tex
Rearrange figures
Cite pointer-generator paper

Captions for news images, such as the example in Figure~\ref{fig:teaser},
typically contain details which cannot be derived from the image alone. They
also frequently contain proper nouns such as names of people, places, and
organisations -- in many cases these proper nouns are rare (most people and
places do not have many news articles written about them). A system capable of
generating high quality news captions should therefor make extensive use of the
provided context and be tuned for generating rare proper nouns. Existing
approaches to news image captioning~\cite{Tariq2017ACE,
Ramisa2016BreakingNewsAA,
	Biten2019GoodNews}  rely on text extraction or
template filling to deal with rare contextual terms such as names of people and
organisations. This makes them relatively inflexibility and means they cannot
be trained end-to-end. Moreover, existing approaches do not include specialised
visual models for frequent nouns -- experiments on the MSCOCO dataset have
shown
that pre-trained object detectors tuned for frequent nouns
lead to more accurate captions~\cite{}.

@@

In this paper we carefully consider the news image captioning problem and
select a set of modelling tools which we combine into a novel architecture that
sets a new state-of-the-art result. Our main contributions are threefold:

@@

   \item We build a captioning model that combines the power of transformers,
   byte-pair encoding, and attention over three different modalities (text,
   images, and faces). We show that our model achieves state-of-the-art results
   with a significant margin over previous methods, and in particular, it can
   generate names not seen during training without the use of templates.

>>>>

Captions for news images, such as the example in Figure~\ref{fig:teaser},
typically contain details which cannot be derived from the image alone. They
also frequently contain proper nouns such as names of people, places, and
organizations -- in many cases these proper nouns are rare (most people and
places do not have many news articles written about them). A system capable of
generating high quality news captions should therefor make extensive use of the
provided context and be tuned for generating rare proper nouns. Existing
approaches to news image captioning~\cite{Tariq2017ACE,
Ramisa2016BreakingNewsAA,
	Biten2019GoodNews}  rely on text extraction or
template filling to deal with rare contextual terms such as names of people and
organizations. This makes them relatively inflexibility and means they cannot
be trained end-to-end. Moreover, existing approaches do not include specialized
visual models for frequent nouns -- experiments on the MSCOCO dataset have
shown
that pre-trained object detectors tuned for frequent nouns
lead to more accurate captions~\cite{}.

@@

In this paper we carefully consider the news image captioning problem and
select a set of modeling tools which we combine into a novel architecture that
sets a new state-of-the-art result. Our main contributions are threefold:

@@

   \item We build a captioning model that combines the power of transformers,
   byte-pair encoding, copying via multi-headed attention, and attention over
   three different modalities (text, images, and faces). We show that our model
   achieves state-of-the-art results with a significant margin over previous
   methods, and in particular, it can generate names not seen during training
   without the use of templates.
